---
title: "rmp-scraper"
output: html_document
date: "2024-08-21"
---

## Load the libraries

To run RSelenium, the Java Development Kit (JDK) must be installed first

```{r}
library(tidyverse)
library(RSelenium)
```

## Create Selenium Driver object

```{r}
rs_driver_object <- rsDriver(browser = "firefox")
```

## Access the client object

```{r}
remDr <- rs_driver_object$client
```

## Start the browser

```{r}
remDr$open()
```

## Create an empty data frame to append the data to

```{r}
all_reviews <- data.frame(Professor_Name = NA,
                          Department = NA,
                          Quality = NA,
                          Difficulty = NA,
                          Class_Name = NA, 
                          Comment = NA)
```

## Navigate to the list of the professors

```{r}
remDr$navigate("https://www.ratemyprofessors.com/search/professors/1439?q=*")
```

## Click on the Close button

```{r}
remDr$findElement(using = "xpath", "//div[starts-with(@class, 'FullPageModal__')]//button")$clickElement()
```

## Navigate to a professor's rating

```{r}
remDr$navigate("https://www.ratemyprofessors.com/professor/324014")
```

## Click the "Load More Ratings" button to show all reviews

```{r}
# find number of ratings 
num_of_ratings <- remDr$findElement(using = 'xpath', "//a[@href='#ratingsList']")$getElementText() %>% 
  unlist() %>% 
  str_extract("[:digit:]+") %>% 
  as.numeric()

# determine how many times to click the "Load More Ratings" button
num_of_iterations <- ceiling( (num_of_ratings - 20) / 10)

if (num_of_iterations > 1) { 
  for (i in 1:num_of_iterations) {
    # click to load more ratings
    load_more <- remDr$findElement(using = "xpath", "//button[text()='Load More Ratings']")
    y_position <- load_more$getElementLocation()$y - 100 # determine y position of element - 100
    remDr$executeScript(sprintf("window.scrollTo(0, %f)", y_position)) # scroll to the element
    load_more$clickElement() # click the element
    Sys.sleep(1.5) # pause code for one and half seconds
  }
}
```

## Extract Name, Department

```{r}
# find teacher name 
professor_name <- remDr$findElement(using = "xpath", "//div[starts-with(@class, 'NameTitle__Name')]")$getElementText() %>%
  unlist()

# department 
department <- remDr$findElement(using = "xpath", "//div[starts-with(@class, 'NameTitle__Title')]//span//b")$getElementText() %>% 
  unlist()
```

## Locate the rating body using xpath

```{r}
rating_body <- remDr$findElements(using = 'xpath', "//div[starts-with(@class, 'Rating__RatingBody')]")
```

## Collect review function

```{r}
collect_review <- function(rating) {
  quality <- rating$findChildElement(using = "xpath", "(.//div[starts-with(@class, 'CardNumRating')])[3]")$getElementText() %>% 
    unlist() %>% 
    as.numeric()
  
  difficulty <- rating$findChildElement(using = "xpath", "(.//div[starts-with(@class, 'CardNumRating')])[6]")$getElementText() %>%
    unlist() %>%
    as.numeric()
  
  class_name <- rating$findChildElement(using = "xpath", "(.//div[starts-with(@class,'RatingHeader__StyledClass')])[2]")$getElementText() %>% 
    unlist()
  
  comment <- rating$findChildElement(using = "xpath", ".//div[starts-with(@class, 'Comments__StyledComments')]")$getElementText() %>% 
    unlist()
  
  return(list(Professor_Name = professor_name, 
              Department = department,
              Quality = quality,
              Difficulty = difficulty, 
              Class_Name = class_name, 
              Comment = comment)) 
}
```

## Apply function to all reviews and append to *all_reviews* dataframe

```{r}
# run the function on all reviews 
reviews <- rating_body %>% map_dfr(~collect_review(.))

# append the reviews to the main dataframe 
all_reviews <- bind_rows(all_reviews, reviews)
```

```{r}
print(all_reviews)
```


# **Running the entire program**

## Loop to click on the "Show More" button

```{r}
# initialize empty dataframe
all_reviews <- data.frame(Professor_Name = NA,
                          Department = NA,
                          Quality = NA,
                          Difficulty = NA,
                          Class_Name = NA, 
                          Comment = NA)

# return to main page
remDr$navigate("https://www.ratemyprofessors.com/search/professors/1439?q=*")
```

## Loop to click on "show more" professors

```{r}
for (t in 1:10) {
  show_more <- remDr$findElement(using = "xpath", "//button[text()='Show More']")
  y_position <- show_more$getElementLocation()$y - 100
  remDr$executeScript(sprintf("window.scrollTo(0, %f)", y_position))  
  show_more$clickElement()
  Sys.sleep(1.5) 
}
```

## Locate teacher card

```{r}
# locates all teacher cards displayed
teacher_cards <- remDr$findElements(using = "xpath", "//a[starts-with(@class, 'TeacherCard__StyledTeacherCard')]")

# extracts urls from teacher cards. We will need these URLs to loop over the data.
teacher_urls <- map(teacher_cards, ~.$getElementAttribute("href") %>% unlist())
```

## The main loop which loops through the professors and collects all their reviews

```{r}
for (t_url in teacher_urls) {

  # navigate to professor's page
  remDr$navigate(t_url)
  
  # a check for skipping over professors with no ratings
  rating_check <- remDr$findElement(using = "xpath", "//div[starts-with(@class,'RatingValue__NumRatings')]")$getElementText() %>% 
    unlist()
  if (rating_check == "No ratings yet. Add a rating.") { next }
  
  # find teacher name 
  professor_name <- remDr$findElement(using = "xpath", "//div[starts-with(@class, 'NameTitle__Name')]")$getElementText() %>% 
    unlist()
  
  # department 
  department <- remDr$findElement(using = "xpath", "//div[starts-with(@class, 'NameTitle__Title')]//span//b")$getElementText() %>% 
    unlist()
  
  # university 
  university <- remDr$findElement(using = "xpath", "//div[starts-with(@class, 'NameTitle__Title')]//a")$getElementText() %>%
    unlist()
  
  # find number of ratings 
  num_of_ratings <- remDr$findElement(using = 'xpath', "//a[@href='#ratingsList']")$getElementText() %>% 
    unlist() %>% 
    str_extract("[:digit:]+") %>% 
    as.numeric()
  
  # determine how many times to click the "Load More Ratings" button
  num_of_iterations <- ceiling((num_of_ratings - 20) / 10)
  
  if (num_of_iterations > 1) { 
    for (i in 1:num_of_iterations) {
      # click to load more ratings
      load_more <- remDr$findElement(using = "xpath", "//button[text()='Load More Ratings']")
      
      y_position <- load_more$getElementLocation()$y - 100 # determine y position of element - 100
      remDr$executeScript(sprintf("window.scrollTo(0, %f)", y_position)) # scroll to the element
      load_more$clickElement() # click the element
      Sys.sleep(1) # pause code for one second
    }
  }
  
  # locate the rating body 
  rating_body <- remDr$findElements(using = 'xpath', "//div[starts-with( @class, 'Rating__RatingBody')]")
  
  # run the function on all reviews 
  reviews <- rating_body %>% map_dfr(~collect_review(.))
  
  # append the reviews to the main dataframe 
  all_reviews <- bind_rows(all_reviews, reviews)
  
  # five second pause before it moves to the next professor 
  Sys.sleep(5)
}
```

## View the data

```{r}
all_reviews %>% as_tibble()
```

## Remove first row of NAs

```{r}
all_reviews <- slice(all_reviews, -1)
```

## Writing the dataset to a file

```{r}
write_csv(all_reviews, "rmp-reviews.csv")
```

## Terminate the selenium server

```{r}
# system("taskkill /im java.exe /f")
system('pkill -f java')
```